### 2017-05-30 paper.tex
Incorporating recent changes

%% Include all macros below
\newcommand{\rulemajor}[1]{\section{#1}}
\begin{document}
\vspace*{0.2in}

@@

FIXME: abstract

@@

FIXME: author summary

@@

FIXME: fill in introduction

@@

FIXME: This is a good place to talk about discoverability as well as licensing

@@

\rulemajor{Point to alternate resources.}

\item
  FIXME: The lesson is a beginning, not an end, so point them at similar material and where to go next.

\item
  FIXME: Make it part of a much broader conversation.

@@

If there are several complementary ways to explain something,
or several points of views that can cohabit respectfully,
it may be possible to present them side by side.
There are actually good pedagogical reasons to do this even if contributors *don't* disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one (FIXME: cite choral explanations).

@@

FIXME

>>>>

%% Include all macros below
\newcommand{\fixme}[2]{\textsc{\textbf{FIXME {#1}: {#2}}}}
\newcommand{\rulemajor}[1]{\section{#1}}
\begin{document}
\vspace*{0.2in}

@@

\fixme{61}{Write abstract}

@@

\fixme{62}{Write author summary}

@@

\fixme{63}{Complete the introduction}

@@

\fixme{64}{Discuss discoverability as well as licensing}

@@

\rulemajor{Link to other resources.}

Most learners are unlikely to absorb everything there is to know about a topic
from your lesson alone.
This is partly a matter of scope---any interesting subject is too large
to fit in a single lesson---but also a matter of level and direction.
As Caulfield has argued \cite{choral-explanations},
the best resources provide a chorus of explanations
that offer many angles and approaches for any given topic,
each of which may be the best fit for a different subset of people.

Find these resources and direct learners to them at strategic points.
These resources may include textbooks,
technical documentation,
videos,
and web pages;
if a community or discussion forum exists for the topic,
be sure to include them as well.

Doing this is a lot of work,
and maintaining it is even more,
which makes building community around lessons (Rule~2) all the more important.
In particular,
it is vital to engage the learners as equal participants in that community:
they should both be able to propose updates, corrections, and additions to lessons,
and know that they are encouraged to do so (Rule~5).

@@

If there are several complementary ways to explain something,
or several points of views that can cohabit respectfully,
it may be possible to present them side by side.
There are actually good pedagogical reasons to do this even if contributors *don't* disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one \cite{choral-explanations}.

@@

\fixme{65}{Write conclusion}
